Title

### 2024-07-02 paper/main.tex
Updates

\begin{enumerate}
	\item \textbf{Make Obvious Mistakes:} Although most algorithms are
		theoretically consistent asymptotically, their finite sample
		properties are not well understood. Moreover, depending on the
		selected hyperparameters, their output can vary significantly.
		These issues combined with no good method to test the
		performance of these algorithms on a given dataset, in
		real-world settings with finite samples, these algorithms can
		make obvious mistakes. Consequently, researchers have to rely on
		posthoc modifications to the model based on their domain
		expertise.
	\item \textbf{Outputs Markov Equivalence Class (MEC):} Multiple
		DAGs can be faithful to a given observational dataset. Thus,
		using only observational data, algorithms can only recover the
		MECs that can contain a combination of directed and undirected
		edges. However, most methods for downstream tasks, such as
		identification or causal effect estimation, assume knowledge of
		a fully oriented DAG. As a result, researchers have to manually
		orient these edges before using them for analysis.
\end{enumerate}

@@

The rest of the paper is structured as follows. In
Section~\ref{sec:background}, we give a background on the measures of
association for various data types. In Section~\ref{sec:mixed_association}, we
present our method for computing mixed data association. In
Section~\ref{sec:modification} and Section~\ref{sec:}, we present how to use
this method to make modifications and the web tool, and lastly in
Section~\ref{sec:empirical}, we show some empirical analysis on how well this
modification process works.

>>>>

\begin{enumerate}
	\item \textbf{Make Obvious Mistakes:} Although most algorithms are
		theoretically consistent asymptotically, their finite sample
		properties are not well understood. Moreover, depending on the
		selected hyperparameters, their output can vary significantly.
		These issues combined with no good method to test the
		performance of these algorithms on a given dataset, in
		real-world settings with finite samples, these algorithms can
		make obvious mistakes. Consequently, researchers have to rely on
		posthoc modifications to the model based on their domain
		expertise.
	\item \textbf{Outputs Markov Equivalence Class (MEC):} Multiple
		DAGs can be faithful to a given observational dataset. Thus,
		using only observational data, algorithms can only recover the
		MECs that can contain a combination of directed and undirected
		edges. However, most methods for downstream tasks, such as
		identification or causal effect estimation, assume knowledge of
		a fully oriented DAG. As a result, researchers have to manually
		orient these edges before using them for analysis.
\end{enumerate}
\todo[inline]{The second point doesn't seem to be adding much}

@@

The rest of the paper is structured as follows. In
Section~\ref{sec:background}, we give a background on the measures of
association for various data types. In Section~\ref{sec:mixed_association}, we
present our method for computing mixed data association. In
Section~\ref{sec:modification} and Section~\ref{sec:web}, we present how to use
this method to make modifications and the web tool, and lastly in
Section~\ref{sec:empirical}, we show some empirical analysis on how well this
modification process works.
